% SIAM Article Template
\documentclass[review,onefignum,onetabnum]{siamart171218}



\input{ex_shared}


\begin{document}

\maketitle
% REQUIRED
\begin{abstract}
This paper describes a new algorithm for computing a low-Tucker-rank approximation of a tensor.
The method applies a randomized linear map to the tensor to obtain a \emph{sketch}
that captures the important directions within each mode, as well as the interactions among the modes.
The sketch can be extracted from streaming or distributed data or with a single pass over the tensor,
and it uses storage proportional to the degrees of freedom in the output Tucker approximation.
The algorithm does not require a second pass over the tensor, although it can exploit another view
to compute a superior approximation. The paper provides a rigorous theoretical guarantee
on the approximation error. Extensive numerical experiments show that that the algorithm
produces useful results that improve on the state of the art for streaming Tucker decomposition.
\end{abstract}

%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}

% REQUIRED
\begin{keywords}
Tucker decomposition, tensor compression, dimension reduction, sketching method, randomized algorithm, streaming algorithm
\end{keywords}

% REQUIRED
\begin{AMS}
  68Q25, 68R10, 68U05
\end{AMS}

\input{introduction.tex}
\input{methodology.tex}
\input{main_theory.tex}
\input{numerical_experiments.tex}
% \input{conclusion.tex}
\section*{Acknowledgments}
MU, YS, and YG were supported in part by DARPA Award FA8750-17-2-0101.
JAT gratefully acknowledges support from ONR Awards N00014-11-10025, N00014-17-12146, and N00014-18-12363.
The authors wish to thank Osman Asif Malik and Stephen Becker for their help
in understanding and implementing Tucker TensorSketch,
and Tamara Kolda for insightful comments on an early draft.

% bibliography
\clearpage
\bibliographystyle{siamplain}
\bibliography{bibtex}

\appendix
\input{Appendix.tex}
\end{document}
